BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-31 Paper/D5.5/D5.5.tex
Added Florent to authors.
Incremented version number for release.

\bibliographystyle{plain}
\begin{document}
\devnum{5.5}
\title{BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications}
\version{0.5}
\deadline{18}
\level{RE}
\nature{Report}
\coordinator{CNRS}
\contributors{Thierry Deutsch (CEA), Luigi Genovese (CEA), Jean-François Méhaut (UJF), Kevin Pouget (CNRS), Brice Videau (CNRS)}
\reviewers{Olivier Aumage (INRIA), Frédéric Desprez (INRIA), Harald Servat (BSC)}
\keywords{BOAST, Deliverable}

@@

\begin{changelog}
\change{0.1}{Initial version of the deliverable}
\change{0.2}{First version sent to reviewers}
\change{0.3}{With corrections from reviewers}
\change{0.4}{Additional corrections from reviewers}
\end{changelog}

>>>>

\bibliographystyle{plain}
\begin{document}
\devnum{5.5}
\title{BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications}
\version{1.0}
\deadline{18}
\level{RE}
\nature{Report}
\coordinator{CNRS}
\contributors{Florent Bouchez Tichadou (UJF), Thierry Deutsch (CEA), Luigi Genovese (CEA), Jean-François Méhaut (UJF), Kevin Pouget (CNRS), Brice Videau (CNRS)}
\reviewers{Olivier Aumage (INRIA), Frédéric Desprez (INRIA), Harald Servat (BSC)}
\keywords{BOAST, Deliverable}

@@

\begin{changelog}
\change{0.1}{Initial version of the deliverable}
\change{0.2}{First version sent to reviewers}
\change{0.3}{With corrections from reviewers}
\change{0.4}{Additional corrections from reviewers}
\change{1.0}{Version to be sent to the EU}
\end{changelog}
